\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-06-26 doc/sui14/relatedwork.tex
commenting on relatedwork“

\subsection{Markers and Vision Methods}
\achal{Not sure where to put this, feel free to move.}
\changes{Many alternative solutions for detecting devices in contained spaces
rely on passive tags on devices, combined with computer vision methods for
detection. Unfortunately, these methods either impose significant constraints
on the camera used for detection, or require large, obtrusive tags, and
inevitably lack feedback from passive devices in the environment. \cite{Bokode},
for example, relies on visually imperceptible codes, but has significant
drawbacks: despite using a 12.1 megapixel DSLR camera, detections are no
longer robust past an angle of 20. Similarly, in our experiments, we found
that striking a balance between the size of the tag, the prices of the
device, and the computational cost of detection was unfeasible with current
cameras and algorithms.}

>>>>

\subsection{Markers and Vision Methods}
\achal{Not sure where to put this, feel free to move.}
\ben{For CV, I think related work is one option to go; however, the requirement of being related work is that -- we need to reference them. There are a few examples ``require large, obtrusive tags, and inevitably lack feedback from passive devices in the environment'' which should be referenced. That's why I am thinking of putting this to discussion.}
\changes{Many alternative solutions for detecting devices in contained spaces
rely on passive tags on devices, combined with computer vision methods for
detection. Unfortunately, these methods either impose significant constraints
on the camera used for detection, or require large, obtrusive tags, and
inevitably lack feedback from passive devices in the environment. \cite{Bokode},
for example, relies on visually imperceptible codes, but has significant
drawbacks: despite using a 12.1 megapixel DSLR camera, detections are no
longer robust past an angle of 20. Similarly, in our experiments, we found
that striking a balance between the size of the tag, the prices of the
device, and the computational cost of detection was unfeasible with current
cameras and algorithms.}
